SoK: Defending Against Web Application Attacks: From Research Approaches to Practical Tools

### 2014-11-15 docs/questioning.tex
adding refs in the text, fix in Fig 2

  In this paper, we systematize the existing knowledge on
  various defense mechanisms against code injection attacks by proposing
  a model that highlights the key weaknesses that enable these attacks,
  and provides a common perspective for the different defenses.
  We then categorize and analyze the various defense mechanisms that
  have been developed, based on their accuracy, performance,
  deployment, security, and availability properties.
  We discuss the results of our analysis, with emphasis on factors
  that may hinder the widespread adoption of attack detection
  mechanisms in practice.

@@

Even though the above implementations impose a low computational
overhead, they require significant deployment effort. In particular,
{\sc sql}rand requires the integration of a proxy within the database
server, while Noncespaces and x{\sc js} require modifications on both
the server and the client.

@@

Defenses based on training include some mechanisms that can be easily
circumvented. For example, {\sc didafit} and libAnomaly do not
tag transactions with their corresponding call sites. This can lead
easily to false negatives. For instance, recall the application
mentioned in Section~\ref{sec:attacks}, which will send the password
for a forgetful user via email by executing the following query:

@@

\noindent
Even if the application's administrators have chosen to use
either {\sc didafit} or libAnomaly as protection,
an attacker could bypass them and obtain the
administrator's password via email,
by entering on the form the standard string:
{\tt nosuchuser' OR id = 'admin}. The infected query matches the
signature of the second one above and is therefore accepted.
The problem lies with the call location of the query, not the query alone.

Mechanisms based on signatures that involve elements not only
associated with code statements (e.g., {\sc amnesia} and {\sc
  sd}river) could detect such attacks. Specifically, {\sc sd}river
associates a complete stack trace with the root of an {\sc sql}
statement, thus it can correlate queries with their call sites and
detect attacks like the above. Furthermore, training
tools that detect {\sc xss} attacks based on JavaScript injection
would fail to detect mimicry attacks where legitimate scripts can be
executed by attackers, but not in the way intended by the
developers~\cite{APKLM10}.

@@

Table~\ref{tab:comp} shows the performance overhead of each mechanism.
In addition, it indicates if the overhead is incurred at the
server ({\sc s}) or at the client side ({\sc c}). In almost half of
the approaches, 16 out of 35 (45.7\%), the overhead is provided as a
percentage, while in other cases, 7 our of 35 (20\%), the authors
provide the latency (in ms) that their mechanisms add to the
normal execution time of the protected application. Note that in some
cases, the times of normal executions are not provided,
so it is not possible to convert absolute
time measurements to percentage overheads. In 10 cases (28.5\%), the
overhead was either not available ({\sc na}) or not quantified ({\sc
  nq}). For {\sc php aspis}, its authors indicate that with
their mechanism, the execution time is doubled.

@@

Mechanisms in different categories face different deployment issues.
Consider the majority of mechanisms in the policy enforcement
subcategory. In most cases, developers should modify multiple
components to use each mechanism. Specifically, mechanisms like
BrowserShield and {\sc beep} require modifications both on the server
and at the client. Thus, it would be difficult to be
adopted by both browser vendors and application developers. On the
other hand, there are cases where the policies introduced at the
server are enforced at the client side, via a library embedded in the
server's response (i.e., Blueprint). Such an approach is convenient
as no modifications are needed at the client.

Extensive modifications in the application's source
code can also be a reason that can make a mechanism
difficult to use. {\sc sql}rand, {\sc amnesia},
mechanisms of the parse-tree validation
subcategory, and mechanisms of the taint
tracking subcategory are such examples.
In the first three cases, programmers should modify every
code fragment that involves the execution of a query.
In the latter case they should also change
all the code fragments that involve user input handling.

Finally, even though many of the mechanisms that involve
training are easy to deploy, they have a distinct disadvantage.
When the application is altered, mechanisms like {\sc sd}river
and {\sc xss-guard} require a new training phase.
However, with the increased adoption of automated testing
and continuous integration frameworks, this phase could be
easily repeated.

@@

In our discussion of the various mechanisms in Section~\ref{sec:defs}, we
observed that some of them can be bypassed by attackers that know
the internals of their operation.
Still, the design of some mechanisms allows them to
be extended and become immune to the circumvention attacks they are
currently vulnerable to. For example, policy enforcement frameworks
based on JavaScript or {\sc html} rewriting can be extended
to detect attacks that leverage {\tt iframe} tags. This does not apply
to all mechanisms though. In particular, training mechanisms like {\sc
  didafit} and {\sc xss-guard} must be redesigned to detect the
attacks we described in the related sections.

@@

Apart from demonstrating the value of a mechanism, good accuracy tests
may be beneficial per se, leading to more well-designed and robust
defenses. Mechanisms that can be circumvented were not extensively
tested in terms of accuracy. For instance, {\sc didafit} was not
tested at all and {\sc xss-guard}'s testing involved 6 known attacks.
This also applies to some frameworks coming from the taint tracking
subcategory. It is possible that more tests during development would
have led the authors to larger design improvements~\cite{Van14}.

@@

The issue is more acute when the point of detection is at the client.
We saw that many policy enforcement mechanisms that detect attacks at
the browser are not easy to deploy because modifications are needed
both on the server and the client side.
Conversely, it may be possible to deliver
the tools to the user unobtrusively; for example, we saw that
Blueprint enforces policies at the client side by embedding a library
in the server's response to the client. In general, when developing a
new countermeasure, researchers should consider where it
will detect attacks, observe the corresponding deployment
challenges, and try to mitigate them.

@@

To the positive side, some defenses have been extensively tested in
terms of accuracy ({\sc sqlc}heck, {\sc amnesia},
libAnomaly), solve specific problems in an effective way (Blueprint
and the system by Stock et al.) or have a low computational overhead
({\sc dsi} and the system by Phung et al.). There are also cases where
researchers have made their code available ({\sc beep} and {\sc
  sd}river), which can promote the development of better
mechanisms. This argument has been raised by another {\sc s}o{\sc k}
paper~\cite{SPWS13}. Furthermore, testing defenses in a production
setting could also propel their adoption.

>>>>

  In this paper, we systematize the existing knowledge on
  various defense mechanisms against code injection attacks by proposing
  a model that highlights the key weaknesses that enable these attacks,
  and provides a common perspective for the different defenses.
  We then categorize and analyze the various defense mechanisms that
  have been developed, based on their accuracy, performance,
  deployment, security, and availability properties.
  Accuracy is of particular importance, as our findings show that many defense
  mechanisms have been tested in a poor manner. In addition, we observe
  that some mechanisms can be bypassed by attackers with knowledge
  of how the mechanisms work. Finally, we discuss the results
  of our analysis, with emphasis on factors that may hinder
  the widespread adoption of attack detection mechanisms
  in practice.

@@

Even though the above implementations impose a low computational
overhead, they require significant deployment effort. In particular,
{\sc sql}rand~\cite{BK04} requires the integration of
a proxy within the database
server, while Noncespaces and x{\sc js}~\cite{APKLM10}
require modifications on both the server and the client.

@@

Defenses based on training include some mechanisms that can be easily
circumvented. For example, {\sc didafit}~\cite{LLW02}
and libAnomaly~\cite{VMV05} do not tag transactions with their
corresponding call sites. This can lead
easily to false negatives. For instance, recall the application
mentioned in Section~\ref{sec:attacks}, which will send the password
for a forgetful user via email by executing the following query:

@@

\noindent
Even if the application's administrators have chosen to use
either {\sc didafit}~\cite{LLW02} or
libAnomaly~\cite{VMV05} as protection,
an attacker could bypass them and obtain the
administrator's password via email,
by entering on the form the standard string:
{\tt nosuchuser' OR id = 'admin}. The infected query matches the
signature of the second one above and is therefore accepted.
The problem lies with the call location of the query, not the query alone.

Mechanisms based on signatures that involve elements not only
associated with code statements (e.g.,
{\sc amnesia}~\cite{HO05,HO06,HO05b} and
{\sc sd}river~\cite{MS09,MKS09,MKLS11})
could detect such attacks. Specifically, {\sc sd}river
associates a complete stack trace with the root of an {\sc sql}
statement, thus it can correlate queries with their call sites and
detect attacks like the above. Furthermore, training
tools that detect {\sc xss} attacks based on JavaScript injection
would fail to detect mimicry attacks where legitimate scripts can be
executed by attackers, but not in the way intended by the
developers~\cite{APKLM10}.

@@

Table~\ref{tab:comp} shows the performance overhead of each mechanism.
In addition, it indicates if the overhead is incurred at the
server ({\sc s}) or at the client side ({\sc c}). In almost half of
the approaches, 16 out of 35 (45.7\%), the overhead is provided as a
percentage, while in other cases, 7 our of 35 (20\%), the authors
provide the latency (in ms) that their mechanisms add to the
normal execution time of the protected application. Note that in some
cases, the times of normal executions are not provided,
so it is not possible to convert absolute
time measurements to percentage overheads. In 10 cases (28.5\%), the
overhead was either not available ({\sc na}) or not quantified ({\sc
  nq}). For {\sc php aspis}~\cite{PMP11}, its authors indicate that with
their mechanism, the execution time is doubled.

@@

Mechanisms in different categories face different deployment issues.
Consider the majority of mechanisms in the policy enforcement
subcategory. In most cases, developers should modify multiple
components to use each mechanism. Specifically, mechanisms like
BrowserShield~\cite{RDWDE07} and {\sc beep}~\cite{TNH07}
require modifications both on the server
and at the client. Thus, it would be difficult to be
adopted by both browser vendors and application developers. On the
other hand, there are cases where the policies introduced at the
server are enforced at the client side, via a library embedded in the
server's response (i.e., Blueprint~\cite{LV09}).
Such an approach is convenient
as no modifications are needed at the client.

Extensive modifications in the application's source
code can also be a reason that can make a mechanism
difficult to use. {\sc sql}rand~\cite{BK04},
{\sc amnesia}~\cite{HO05,HO06,HO05b},
mechanisms of the parse-tree validation
subcategory, and mechanisms of the taint
tracking subcategory are such examples.
In the first three cases, programmers should modify every
code fragment that involves the execution of a query.
In the latter case they should also change
all the code fragments that involve user input handling.

Finally, even though many of the mechanisms that involve
training are easy to deploy, they have a distinct disadvantage.
When the application is altered, mechanisms like
{\sc sd}river~\cite{MS09,MKS09,MKLS11}
and {\sc xss-guard}~\cite{BV08} require a new training phase.
However, with the increased adoption of automated testing
and continuous integration frameworks, this phase could be
easily repeated.

@@

In our discussion of the various mechanisms in Section~\ref{sec:defs}, we
observed that some of them can be bypassed by attackers that know
the internals of their operation.
Still, the design of some mechanisms allows them to
be extended and become immune to the circumvention attacks they are
currently vulnerable to. For example, policy enforcement frameworks
based on JavaScript or {\sc html} rewriting can be extended
to detect attacks that leverage {\tt iframe} tags. This does not apply
to all mechanisms though. In particular, training mechanisms like {\sc
  didafit}~\cite{LLW02} and {\sc xss-guard}~\cite{BV08} must be
redesigned to detect the atacks we described in the related sections.

@@

Apart from demonstrating the value of a mechanism, good accuracy tests
may be beneficial per se, leading to more well-designed and robust
defenses. Mechanisms that can be circumvented were not extensively
tested in terms of accuracy. For instance, {\sc didafit}~\cite{LLW02}
was not tested at all and {\sc xss-guard}'s~\cite{BV08}
testing involved 6 known attacks.
This also applies to some frameworks coming from the taint tracking
subcategory. It is possible that more tests during development would
have led the authors to larger design improvements~\cite{Van14}.

@@

The issue is more acute when the point of detection is at the client.
We saw that many policy enforcement mechanisms that detect attacks at
the browser are not easy to deploy because modifications are needed
both on the server and the client side.
Conversely, it may be possible to deliver
the tools to the user unobtrusively; for example, we saw that
Blueprint~\cite{LV09} enforces policies at the client side by embedding a library
in the server's response to the client. In general, when developing a
new countermeasure, researchers should consider where it
will detect attacks, observe the corresponding deployment
challenges, and try to mitigate them.

@@

To the positive side, some defenses have been extensively tested in
terms of accuracy ({\sc sqlc}heck~\cite{SW06},
{\sc amnesia}~\cite{HO05,HO06,HO05b}, libAnomaly~\cite{VMV05}),
solve specific problems in an effective way
(Blueprint~\cite{LV09} and the system by Stock et al.~\cite{SLMS14}) or
have a low computational overhead
({\sc dsi}~\cite{NSS06} and the system by Phung et al.~\cite{PSC09}).
There are also cases where
researchers have made their code available ({\sc beep}~\cite{TNH07}
and {\sc sd}river~\cite{MS09,MKS09,MKLS11}),
which can promote the development of better
mechanisms. This argument has been raised by another {\sc s}o{\sc k}
paper~\cite{SPWS13}. Furthermore, testing defenses in a production
setting could also propel their adoption.
